Sequential rank agreement methods for comparison of ranked lists

### 2015-04-27 latex/paper.Rnw
Manuskript

\begin{document}
%\SweaveOpts{concordance=TRUE}

@@

\texttt{FIXME: Skal der et specifikt eksempel ind her eller kan vi
  bare bruge det fra senere?}

\subsection{Analysis of incomplete/censored lists}
Not uncommon for lists to be

@@

\begin{figure}[tb]
\begin{center}
<<fig=TRUE,echo=FALSE,width=3>>=
ysize <- 1000
plot(res[1:ysize], lwd=3, col="red", type="l", ylim=c(0,1300), ylab="Sequential rank agreement", xlab="Depth")
lines(res2[1:ysize], lwd=2, col="purple")
## 
# col1 <- makeTransparent()
null <- sqrt(random_list_sra(inputmatrix, B=1, n=400))
null3 <- sqrt(random_list_sra(inputmatrix, B=20, n=200))
## matlines(null[1:ysize,], col="gray", lty=1)

@@

<<fig=TRUE,echo=FALSE,width=3>>=
ysize <- 100
plot(res[1:ysize], lwd=3, col="red", type="l", ylim=c(0,1300), ylab="Sequential rank agreement", xlab="Depth")
lines(res2[1:ysize], lwd=2, col="purple")
## 
# col1 <- makeTransparent()
null <- sqrt(random_list_sra(inputmatrix, B=1, n=400))
null3 <- sqrt(random_list_sra(inputmatrix, B=20, n=200))
## matlines(null[1:ysize,], col="gray", lty=1)

@@

@ %
\end{center}
 \caption{Sequential rank agreement for 4 different analysis methods
   applied to the Golub data (thick red line). The red and blue shaded
 areas represent the pointwise 95\% normal areas for the XXX and XXY benchmarks,
respectively.}
 \label{fig:example1}
\end{figure}

@@

<<>>=
library(changepoint)
cpt.mean(res, method="BinSeg")
cpt.mean(res2)
@

>>>>

\SweaveOpts{prefix.string=paper, keep.source=TRUE}

\begin{document}

@@

\begin{figure}[tb]
\begin{center}
\includegraphics[width=.45\textwidth]{paper-fig1a}
\includegraphics[width=.45\textwidth]{paper-fig1b}
\end{center}
 \caption{Sequential rank agreement for 4 different analysis methods
   applied to the Golub data (thick red line). The red and blue shaded
 areas represent the pointwise 95\% normal areas for the XXX and XXY benchmarks,
respectively.}
 \label{fig:example1}
\end{figure}

\subsection{Analysis of incomplete/censored lists}
Incomplete lists are also a common occurrence that arise from, for
example, comparison of top $k$ lists, when some methods only rank some
of the items (e.g., penalized regression based on the Lasso provides a
sparse set of predictors that have non-zero coefficients. There is no
obvious ordering of the predictors that have been shrunk to zero), or
if

Top $k$, methods only provide information on some ranking (Lasso),
only interested in significant ...predictors

@@

<<fig1a, fig=TRUE,echo=FALSE,include=FALSE>>=
ysize <- 1000
plot(res[1:ysize], lwd=3, col="red", type="l", ylim=c(0,1300), ylab="Sequential rank agreement", xlab="Depth")
lines(res2[1:ysize], lwd=2, col="purple")

<<fig1b, fig=TRUE,echo=FALSE,include=FALSE >>=
ysize <- 80
plot(res[1:ysize], lwd=3, col="red", type="l", ylim=c(0,1300), ylab="Sequential rank agreement", xlab="Depth")
lines(res2[1:ysize], lwd=2, col="purple")

<<fig2a, fig=TRUE,echo=FALSE,include=FALSE>>=
ysize <- 1000
plot(res[1:ysize], lwd=3, col="red", type="l", ylim=c(0,1300), ylab="Sequential rank agreement", xlab="Depth")
lines(res2[1:ysize], lwd=2, col="purple")
## 
# col1 <- makeTransparent()
null <- sqrt(random_list_sra(inputmatrix, B=1, n=400))
null3 <- sqrt(random_list_sra(inputmatrix, B=20, n=200))
## matlines(null[1:ysize,], col="gray", lty=1)

@@

<<fig2b, fig=TRUE,echo=FALSE,include=FALSE >>=
ysize <- 80
plot(res[1:ysize], lwd=3, col="red", type="l", ylim=c(0,1300), ylab="Sequential rank agreement", xlab="Depth")
lines(res2[1:ysize], lwd=2, col="purple")
## 
# col1 <- makeTransparent()
null <- sqrt(random_list_sra(inputmatrix, B=1, n=400))
null3 <- sqrt(random_list_sra(inputmatrix, B=20, n=200))
## matlines(null[1:ysize,], col="gray", lty=1)

@@

\begin{figure}[tb]
\begin{center}
\includegraphics[width=.45\textwidth]{paper-fig2a}
\includegraphics[width=.45\textwidth]{paper-fig2b}
\end{center}
 \caption{Sequential rank agreement for 4 different analysis methods
   applied to the Golub data (thick red line). The red and blue shaded
 areas represent the pointwise 95\% normal areas for the XXX and XXY benchmarks,
respectively.}
 \label{fig:example1}
\end{figure}

@@

<<>>=
library(changepoint)
cp1 <- cpt.mean(res, method="BinSeg")
cp2 <- cpt.mean(res2, method="BinSeg")
cp1@cpts
cp1@param.est
cp2@cpts
cp2@param.est
@
